The Exoplanet Orbit Database \textsc{II}: updates for 2014

### 2014-03-26 draft/ms.tex
Revision 2

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will .

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in units of degrees. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planet transiting star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
the true spin-orbit angle, defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow \cite{Fabrycky2009} where the coordinates are defined as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field to the EOD but we describe it here because we did not
previously report it consistently, since some literature report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{e.g. \cite{Moutou2011}, }. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.

@@

We also report the upper limits (XUL) for planet minimum mass (MSINI),
eccentricity (ECC), and the radial velocity semi-amplitude (K) when
the literature reports them. For example, the upper limits for ECC is
reported when the orbit is consistent with a circular one, and the
upper limits for K is reported when there is only upper-limit radial
velocity detection. If only upper limits are given, we set the
parameter field X to 0, the uncertainty XU to half of the upper limit,
and the upper error bar XUPPER to the upper limits (same as XUL). For
example, if the literature reports the upper limit for ECC, which we
report in ECCUL, then we set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:}

@@

% Other Planets
Second, we now also include robustly detected imaging, microlensing,
and timing planets, and our criteria for a `robust detection' are the
following (as set by the QUACBED):

@@

@@

In the future, we hope to include images of directly imaged planets
(where allowed under copyright law) and light curves for transits and microlensing planets. We
also plan to display RV curves whenever their RV data are available and include better incorporation of Kepler parameters in the EOD (such as KEPID). We also want upper limits in the EDE table and plotter.

@@

NSF funding?

@@

>>>>

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will reveal it.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in units of degrees. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planet transiting star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
the true spin-orbit angle, defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow \cite{Fabrycky2009} where the coordinates are defined as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field to the EOD but we describe it here because we did not
previously report it consistently, since some literature report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, e.g. \cite{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.

@@

We also report the upper limits (XUL) for planet minimum mass (MSINI),
eccentricity (ECC), and the radial velocity semi-amplitude (K) when
the literature reports them. For example, the upper limits for ECC is
reported when the orbit is consistent with a circular one, and the
upper limits for K is reported when there is only upper-limit radial
velocity detection. If only upper limits are given, we set the
parameter field X to 0, the uncertainty XU to half of the upper limit,
and the upper error bar XUPPER to the upper limits (same as XUL). For
example, if the literature reports the upper limit for ECC, which we
report in ECCUL, then we set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:website}

@@

% Other Planets
Second, we now also include robustly detected imaging, microlensing,
and timing planets, and our criteria for a `robust detection' are the
following:

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/senew.eps}
\caption{An example plot that demonstrates the current secondary eclipse measurements. Each planet has a set of circles that stand for its available secondary eclipse measurements in the database, including Spitzer 8.0, 5.8, 4.5, \& 3.6 $\mu m$, and  ground-based $J$, $H$, and $Ks$ bands. \kepler\ secondary eclipse measurements are labeled as solid black dots. A few representative planets are also annotated.}
\label{fig:se}
\end{figure}

@@

In the future, we hope to include images of directly imaged planets
(where allowed under copyright law) and light curves for transits and microlensing planets. We plan to display RV curves whenever their RV data are available and include better incorporation of Kepler parameters in the EOD (such as KEPID). We also hope to include upper limits in the EDE table and plotter.

@@

NSF funding? ZZZ will be added by Jason

@@

CEHW, SIMBAD, EA, and JS acknowledgement
